# Week 3 Short Answer Questions

## Brett Graham

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

5.1
```{r}
library(mosaicData)
```


5.2
```{r}
WorldMap(HappinessIndex,key = "country" , fill = "corruption")
```

6.5
States and Polling Organizations

6.6
D. Rectangle. Graphical attribute: color and text.

6.7
D. NYT poll probability for the Democratic candidate.

6.8
```{r}
Small <-
  NCHS %>%
  sample_n(size=5000)
```

The frame shows the relationship between bmi and weight. The specific glyph on the plot is a cirle that denotes whether or not the person is a smoker.

7.1
a. Mean()
b. Variable1 / Variable2
c. rank()
d. filter()
e. %>% datatable groupby(A,X)
f. datatable %>% groupby(A,B) %>% summarise(value = max(X))

7.4
a. The argumenet in group_by should not have quotes. 
b. summarise() needs an equals sign in the argument.

7.5
a. group_by(BabyNames, sex)
b. filter(BabyNames, sex=="F")
c. BabyNames %>% group_by(sex) %>% filter(count > 20)
d. summarise(BabyNames, total = sum(count))
e. BabyNames %>% group_by(name,count)


7.11
a. sex, count, meanAge
b. diagnosis, count, meanAge
c. sex, diagnosis, count , meanAge
d. Age, diagnosis, count, meanAge
e. Age, count, meanAge